### 2024-11-07 Manuscript/main_ecography_R1.tex
Update main_ecography_R1.tex

The ability of different metrics to capture the different patterns (and thus approximate the processes) was highly variable.
It ranged from metrics capturing no clear pattern (e.g. the Functional evenness based on the dendrogram method for competition) to metrics clearly capturing one specific pattern (e.g. Divergence based on probability density for the equalising mechanism for a decrease in space occupancy).
Although most metrics captured a decrease in metric score relative to the amount of removed data, some metrics resulted into a score increase (e.g. the functional evenness based on hypervolume for the equalising mechanism) or non-linear responses (e.g. Alpha diversity based on dendrogram for the equalising mechanism).
Some cases resulted in an increase in metric score relative to random removals (positive values in Figure \ref{Fig:simulation_results}).

>>>>

The ability of different metrics to capture the different patterns (and thus approximate the mechanisms) was highly variable.
It ranged from metrics capturing no clear pattern (e.g. the Functional evenness based on the dendrogram method for competition) to metrics clearly capturing one specific pattern (e.g. Divergence based on probability density for the equalising mechanism for a decrease in space occupancy).
Although most metrics captured a decrease in metric score relative to the amount of removed data, some metrics resulted into a score increase (e.g. the functional evenness based on hypervolume for the equalising mechanism) or non-linear responses (e.g. Alpha diversity based on dendrogram for the equalising mechanism).
Some cases resulted in an increase in metric score relative to random removals (positive values in Figure \ref{Fig:simulation_results}).
Furthermore, although we predicted some more common changes in aspects of functional diversity for some specific mechanisms, our simulation show that most metrics under most aspects (richness, divergence or regularity) capture changes of trait space occupancy under any mechanism (see caveats section in the discussion).
